Scaffolder - Simple and reproducible genome scaffolding using text configuration files.

### 2011-01-12 text/src/article.tex
Revise abstract and title

\title{Scaffolder - Simple and reproducable genome scaffolding using
text configuration files.}

@@

\begin{abstract}
  \paragraph*{Background:} Background \dots
  \paragraph*{Methods:} Methods \dots
  \paragraph*{Results:} Results \ldots
  \paragraph*{Conclusions:} Conclusions \ldots
\end{abstract}

>>>>

\title{Scaffolder - Simple and reproducible genome scaffolding using
text configuration files.}

@@

\begin{abstract}

  \paragraph*{Background:} Assembly of short read sequencing data can result in
  a fragmented series of contigs. Therefore a common step in a genome project
  is piece separate contigs together and fill gaps generated by PCR. This
  scaffolding step however is non-trivial requiring manipulation of large
  blocks of nucleotide sequence. Manually joining contigs also hides the source
  of each region in the final genome fasta file. Taken together these
  considerations make reproducing or editing an existing genome build
  difficult.

  \paragraph*{Methods:} The software outlined "Scaffolder" is implemented in
  the ruby programming language and installed via the RubyGems software
  management system. Genome scaffolds are defined using YAML - a markup
  language which is both human and machine readable. Command line binaries and
  extensive documentation are also available for the package.

  \paragraph*{Results:} This software allows a genome build to be defined in
  terms of the constituent contigs using a relatively simple to write and edit
  scaffold file syntax. This scaffold file defines where each contig is used
  making the genome build reproducible and comparatively easier to edit than
  fasta sequence. This syntax also supports adding inserts to the scaffold for
  the purpose of bridging gaps or replace regions.

  \paragraph*{Conclusions:} Scaffolder is easy to use genome scaffolding
  software. This tool promotes reproducibility and maintenance in building
  a genome. Scaffolder can be found at http://michaelbarton.me.uk/sfdr.

\end{abstract}
